Enhancement of SDR in Thessaloniki

### 2024-01-22 GHI_enh_04_investigate.tex
Commit 2024-01-21 22:14
Commit 2024-01-22 10:14
Commit 2024-01-22 12:14

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-01-21}

@@

Arima: -0.1679 3.8751 -0.0433 0.9654

@@

Arima: 28.0362 4.3654 6.4224 0

@@

@@

@@

@@

\begin{verbatim}
2024-01-21 11:10:50.8 athan@tyler GHI_enh_04_investigate.R 1.035152 mins
\end{verbatim}

>>>>

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-01-22}

@@

Arima: -0.1679 3.8757 -0.0433 0.9654

@@

Arima: 28.0362 4.3653 6.4225 0

@@

@Zhang2018

@@

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-4} \end{center}

@@

@Martins2022

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/energy-5} \end{center}

@@

\begin{verbatim}
2024-01-22 08:48:56.1 athan@sagan GHI_enh_04_investigate.R 0.252639 mins
\end{verbatim}
